SMT-COMP 2021\\ 17th International Satisfiability Modulo Theory Competition

### 2022-08-11 2022/slides/smtWorkshop/slides.tex
slides

%%% Titel, Autor und Datum des Vortrags:
\title{SMT-COMP 2021\\
16th International Satisfiability Modulo Theory Competition}
\author{Haniel Barbosa \and \emph{Jochen Hoenicke} \and Antti Hyv\"arinen}
\date{July 18, 2021}

%% Institut
\institute{
  Universidade Federal de Minas Gerais, Brazil \and
  Albert-Ludwigs-Universit\"at Freiburg, Germany \and
  Universita della Svizzera italiana, Switzerland
}

@@

@@

  \begin{minipage}[b]{.6\textwidth}
    Annual competition for \emph{SMT solvers}\\
    on (a selection of) benchmarks from \emph{SMT-LIB}
  \end{minipage}%
  \begin{minipage}{.4\textwidth}
    \begin{block}{History}
      \begin{tabular}{rp{3cm}}
        \textbf{2005} & first competition \\
        \textbf{2013} & evaluation instead \\
        & of competition\\
        \textbf{2014} & since then hosted\\
        & by \emph{StarExec}\\
        \textbf{2021} & 16th competition
      \end{tabular}
    \end{block}
  \end{minipage}

  Goals:
  \begin{itemize}
  \item spur development of SMT solver implementations
  \item promote SMT solvers and their usage
  \item support the SMT-LIB project
    \begin{itemize}
    \item to promote and develop the SMT-LIB format
    \item to collect relevant benchmarks
    \end{itemize}
  \item engage and include new members
  \end{itemize}

@@

  \begin{columns}
    \begin{column}{0.4\textwidth}
      \begin{block}{Non-incremental}
        381\,683 instances {\small (+5082)} \\
        with 1 query each \\
        in 79 logics {\small (+9)}.
      \end{block}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{block}{Incremental}
        43\,284 instances {\small (+19\,073)}\\
        with 33\,998\,794 queries {\small (+554\,499)} \\
        in 35 logics {\small (+2)}.
      \end{block}
    \end{column}
    \begin{column}{0.08\textwidth}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{SMT-LIB Logics}

  \noindent\makebox[\textwidth]{%
  \begin{tikzpicture}[xscale=2.55,yscale=.39]
    \uncover<1-3> {
    % Arith
    \node at (3,14) {\small LIA};
    \node at (3,13) {\small LRA};
    \node at (3,12) {\small NIA};
    \node at (3,11) {\small NRA};
    % Equality
    \node at (3,9) {\small UF};
    \node at (3,8) {\small UFDT};
    % Bitvec
    \node at (3,6) {\small BV};
    % FPArith
    \node at (3,4) {\small BVFP};
    \node at (3,3) {\small BVFPLRA};
    \node at (3,2) {\small FP};
    \node at (3,1) {\small FPLRA};
    % Equality+LinearArith
    \node at (4,15) {\small ALIA};
    \node at (4,14) {\small AUFLIA};
    \node at (4,13) {\small AUFLIRA};
    \node at (4,12) {\small AUFDTLIA};
    \node at (4,11) {\small AUFDTLIRA};
    \node at (5,15) {\small UFDTLIA};
    \node at (5,14) {\small UFDTLIRA};
    \node at (5,13) {\small UFIDL};
    \node at (5,12) {\small UFLIA};
    \node at (5,11) {\small UFLRA};
    % Equality+NonLinearArith
    \node at (4,10) {\small ANIA};
    \node at (4,9) {\small AUFNIA};
    \node at (4,8) {\small AUFNIRA};
    \node at (4,7) {\small AUFDTNIRA};
    \node at (5,10) {\small UFDTNIA};
    \node at (5,9) {\small UFDTNIRA};
    \node at (5,8) {\small UFNIA};
    \node at (5,7) {\small UFNRA};
    % Equality+MachinedArith
    \node at (4,6) {\small ABV};
    \node at (4,5) {\small ABVFP};
    \node at (4,4) {\small ABVFPLRA};
    \node at (4,3) {\small AUFBV};
    \node at (4,2) {\small AUFBVFP};
    \node at (4,1) {\small AUFBVDTLIA};
    \node at (4,0) {\small AUFBVDTNIA};
    \node at (5,6) {\small AUFFPDTLIRA};
    \node at (5,5) {\small AUFFPDTNIRA};
    \node at (5,4) {\small UFBV};
    \node at (5,3) {\small UFBVFP};
    \node at (5,2) {\small UFBVLIA};
    \node at (5,1) {\small UFFPDTLIRA};
    \node at (5,0) {\small UFFPDTNIRA};

    %QF_LinearIntArith
    \node at (0,14) {\small QF\_IDL};
    \node at (0,13) {\small QF\_LIA};
    \node at (0,12) {\small QF\_LIRA};
    %QF_LinearRealArith
    \node at (0,11) {\small QF\_RDL};
    \node at (0,10) {\small QF\_LRA};
    %QF_NonLinearIntArith
    \node at (0,9) {\small QF\_NIA};
    \node at (0,8) {\small QF\_NIRA};
    %QF_NonLinearRealArith
    \node at (0,7) {\small QF\_NRA};
    %QF_Equality
    \node at (0,6) {\small QF\_AX};
    \node at (0,5) {\small QF\_DT};
    \node at (0,4) {\small QF\_UF};
    \node at (0,3) {\small QF\_UFDT};
    %QF_Bitvec
    \node at (0,2) {\small QF\_BV};
    %QF_Strings
    \node at (0,1) {\small QF\_S};
    \node at (1,1) {\small QF\_SLIA};
    \node at (2.05,1) {\small QF\_SNIA};
    %QF_Equality+LinearArith
    \node at (1,14) {\small QF\_ALIA};
    \node at (1,13) {\small QF\_AUFLIA};
    \node at (1,12) {\small QF\_UFIDL};
    \node at (1,11) {\small QF\_UFLIA};
    \node at (1,10) {\small QF\_UFDTLIRA};
    \node at (1,9) {\small QF\_UFLRA};
    %QF_Equality+NonLinearArith
    \node at (1,8) {\small QF\_ANIA};
    \node at (1,7) {\small QF\_AUFNIA};
    \node at (1,6) {\small QF\_UFNIA};
    \node at (1,5) {\small QF\_UFNRA};
    %QF_Equality+Bitvec
    \node at (1,4) {\small QF\_ABV};
    \node at (1,3) {\small QF\_AUFBV};
    \node at (1,2) {\small QF\_UFBV};
    %QF_Equality+Bitvec+Arith
    \node at (2.05,4) {\small QF\_AUFBVLIA};
    \node at (2.05,3) {\small QF\_AUFBVNIA};
    \node at (2.05,2) {\small QF\_UFBVLIA};
    %QF_FPArith
    \node at (2.05,14) {\small QF\_ABVFP};
    \node at (2.05,13) {\small QF\_ABVFPLRA};
    \node at (2.05,12) {\small QF\_AUFBVFP};
    \node at (2.05,11) {\small QF\_BVFP};
    \node at (2.05,10) {\small QF\_BVFPLRA};
    \node at (2.05,9) {\small QF\_FP};
    \node at (2.05,8) {\small QF\_FPLRA};
    \node at (2.05,7) {\small QF\_UFFP};
    \node at (2.05,6) {\small QF\_UFFPDTLIRA};
    }
    %
    \uncover<2-> {
      \draw (2.6,-0.5) -- (2.6,17);
      \node at (1,16.5) {Quantifier-free};
      \node at (4,16.5) {Quantified};
    }
    \uncover<3-> {
      \draw (-.5,.5) rectangle (2.6,1.5);
      \draw (-.5,1.5) rectangle (.5,2.5);
      \draw (-.5,2.5) rectangle (.5,6.5);
      \draw (-.5,6.5) rectangle (.5,7.5);
      \draw (-.5,7.5) rectangle (.5,9.5);
      \draw (-.5,9.5) rectangle (.5,11.5);
      \draw (-.5,11.5) rectangle (.5,14.5);
      \draw (.5,1.5) rectangle (1.5,4.5);
      \draw (.5,4.5) rectangle (1.5,8.5);
      \draw (.5,8.5) rectangle (1.5,14.5);
      \draw (1.5,1.5) rectangle (2.6,5);
      \draw (1.5,5) rectangle (2.6,14.5);

      \draw (2.6,0) rectangle (3.5,5);
      \draw (2.6,5) rectangle (3.5,7);
      \draw (2.6,7) rectangle (3.5,10);
      \draw (2.6,10) rectangle (3.5,15);
      \draw (3.5,-.5) rectangle (5.6,6.5);
      \draw (3.5,6.5) rectangle (5.6,10.5);
      \draw (3.5,10.5) rectangle (5.6,15.5);
    }
    \uncover<4-> {
      \node at (1,15) {QF\_};
      \node at (0,13) {LinearInt};
      \node at (0,10.5) {LinearReal};
      \node at (0,8.5) {NonLinearInt};
      \node at (0,7) {NonLinearReal};
      \node at (0,4.5) {Equality};
      \node at (0,2) {Bitvec};
      \node at (1,11.5) {\begin{tabular}{c}Equality+\\LinearArith\end{tabular}};
      \node at (1,6.5) {\begin{tabular}{c}Equality+\\NonLinearArith\end{tabular}};
      \node at (1,3) {\begin{tabular}{c}Equality+\\Bitvec\end{tabular}};
      \node at (1,1) {String};
      \node at (2,10) {FPArith};
      \node at (2,3) {\begin{tabular}{c}Equality+\\Bitvec+Arith\end{tabular}};
      \node at (1,15) {QF\_};

      \node at (3,12.5) {Arith};
      \node at (3,8.5) {Equality};
      \node at (3,6) {Bitvec};
      \node at (3,2.5) {FPArith};

      \node at (4.5,13) {\begin{tabular}{c}Equality+\\LinearArith\end{tabular}};
      \node at (4.5,8.5) {\begin{tabular}{c}Equality+\\NonLinearArith\end{tabular}};
      \node at (4.5,3){\begin{tabular}{c}Equality+\\MachineArith\end{tabular}};
    }
  \end{tikzpicture}
  }

  \uncover<2-3>{
    \small
    \textbf{Q}uantifier \textbf{F}ree
    \textbf{A}rray
    \textbf{U}ninterpreted \textbf{F}unction
    \textbf{B}it\textbf{V}ector
    \textbf{F}loating\textbf{P}oint
    \textbf{D}ata\textbf{T}ype
    \textbf{S}trings
    \textbf{N}onlinear/\textbf{L}inear
    \textbf{I}nteger \textbf{R}eal
    \textbf{A}rithmetic
    \textbf{D}ifference \textbf{L}ogic
    }
\end{frame}

@@

\begin{frame}[fragile]{SMT-COMP Tracks (new)}
  SMT-COMP 2021 has two new experimental tracks (sponsored by AWS).
  \bigskip

  \emph{Parallel Track}
  \begin{itemize}
  \item Solve a large problem on a big computer
    \begin{itemize}
    \item 64 cores, 256 GB of memory
    \end{itemize}
  \item Solver answers sat/unsat/unknown
  \end{itemize}
  \bigskip
  \emph{Cloud Track}
  \begin{itemize}
  \item Solve a large problem on a network of computers
    \begin{itemize}
    \item 100 machines, 1600 cores, 6400 GB of memory
    \end{itemize}
  \item Solver answers sat/unsat/unknown
  \end{itemize}
\end{frame}

\begin{frame}{Tracks, Solvers, Divisions, and Benchmarks}
  Teams: 18 (+2)
  \bigskip

  \begin{tabular}{c|r@{}l|r@{}l|c}
    Track & \multicolumn{2}{c|}{Solvers} & \multicolumn{2}{c|}{Divisions}  & Benchmarks \\
    \hline
    Single Query  &  19&(-1)  & 18&(-49)  & 101300/381683 \\
    Incremental &  7&(-2)   & 15&(-11)  & 22233/43284   \\
    Unsat Core  &  7&(+2)   & 17&(-23)  & 55463/108188  \\
    Model Validation  &  7&(=)    &  3&(+2) + 3 exp.  & 13301/21251  \\
    Parallel &   &3      &   &14 exp.  & 413/20705 \\
    Cloud & &5      &   &14 exp.  & 405/20669 \\
  \end{tabular}
  \bigskip

  Number in parenthesis shows changes from 2020
\end{frame}

@@

  SMT-COMP 2021 participants:
  \begin{itemize}
  \item classic CDCL(T)-based SMT solvers
  \item mcSAT-based solvers
  \item automated theorem provers
  \item finite domain solver
  \item local search techniques
  \item wrapper extending the scope of existing solvers
  \end{itemize}

  \bigskip
  Four new solvers participated:
  \begin{itemize}
  \item iProver (Konstantin Korovin, Andre Duarte, Edvard K Holden)
  \item mc2 (Simon Cruanes, Guillaume Bury)
  \item YicesLS (Bohan Li, Shaowei Cai, Xindi Zhang)
  \item YicesQS (Stéphane Graham-Lengrand)
  \end{itemize}

@@

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{bitwuzla-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{COLIBRI-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{cvc5-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{cvc5-gg-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{iprover-nonumber.pdf}}
\end{frame}
}

{
\setbeamertemplate{footline}{\quad\hfill\footnotesize\textcolor{white}{\insertframenumber}\strut\kern1em\vskip1pt}
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{mc2-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{opensmt-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{smtinterpol-nonumber.pdf}}
\end{frame}
}

{
%\setbeamertemplate{footline}{\quad\hfill\footnotesize\textcolor{white}{\insertframenumber}\strut\kern1em\vskip1pt}
\begin{frame}<1,3>
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \only<1>{%
      \includegraphics[height=\paperheight,page=1]{smt-rat-nonumber.pdf}
    }\only<2>{%
      \includegraphics[height=\paperheight,page=2]{smt-rat-nonumber.pdf}
    }\only<3>{%
      \includegraphics[height=\paperheight,page=3]{smt-rat-nonumber.pdf}
    }}%
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{UltimateEliminator-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{vampire-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{verit-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}\vspace*{-.1\paperheight}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=1.2\paperheight]{Yices-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{YicesQS-nonumber.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{YicesLS-nonumber.pdf}}
\end{frame}
}

@@

  Submitted by Organisers
  \begin{itemize}
  \item z3-4.8.11
  \item MathSAT 5.6.6
  \item Par4 (for Parallel Track)
  \item Division winners from last year (32 Solvers)
  \end{itemize}
  \bigskip

  Submitted by Participants
  \begin{itemize}
  \item Fixed solvers (Bitwuzla, COLIBRI, cvc5, iProver, OpenSMT, Vampire)
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{New in 2021}

  \begin{itemize}
  \item model validation track extended
  \item manually checking and resolving disagreements
  \item multiple logics per division
  \item we will create an artifact
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Model Validation Track}

  Solvers print model for each constant/uninterpreted function
\begin{verbatim}
sat
(model
  (define-fun x15 () Int 5)
  (define-fun x24 () x135 (as @1 x135))
  (define-fun x10 ((?X1 Int)) Int (ite (and (= ?X1 10)) 2 (ite...
\end{verbatim}

  \begin{itemize}
  \item model validator based on pySMT
  \item all models of the competitors were accepted
  \item validator is still inefficient ($>$ 15 minutes)
  \end{itemize}

  Many thanks to \emph{Andrea Micheli}
\end{frame}

  \begin{itemize}
  \item 111285 instances of 381683 have no status
  \item we checked disagreements between solvers
  \item 209 non-incremental instances
    and 65 incremental instances
  \item only 28 had known sat/unsat status
  \item tactics to resolve status:
    \begin{itemize}
    \item similar disagreements on instances with known status
    \item confirmed with fixed version of participants
    \item analyzed model from solver claiming sat
    \item majority vote
    \item in rare cases manually analyzed instances
    \end{itemize}
  \item solvers found unsound: (Bitwuzla, COLIBRI, cvc5, iProver, MathSAT, OpenSMT, Par4, UltimateEliminator+MathSAT, Vampire, Z3str4)
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Divisions}
  Tracks are split into \emph{divisions}.

  \begin{itemize}
  \item \emph{before 2021}: Division = SMT-LIB logic
  \item \emph{2021}: 19 Divisions subdivided in 84 logics
  \end{itemize}

  This implied more changes:
  \begin{itemize}
  \item solver authors select supported logics
    \begin{itemize}
    \item[$\Rightarrow$] solvers may run on only a part of a division.
    \end{itemize}
  \item fewer winners (1--5 winners per division)
  \item two solvers won a logic but not a division
    \begin{itemize}
    \item YicesQS won NRA
    \item YicesLS won QF\_IDL
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Statistics}
  Solver Size
  \begin{itemize}
  \item range from 930~kB to 196~MB (compressed)
  \item total 436 MB
  \item unsat core post-processor: 361~MB
  \end{itemize}
  \bigskip
  \pause

  Job statistics
  \begin{itemize}
  \item Total Job Size: $\sim$ 85 GB
    \begin{itemize}
    \item 35~GB YicesLS temporary files
    \item 29~GB z3 models
    \end{itemize}
  \item 1\,371\,593 pairs (+428\,000)
  \item 16.3 CPU years (+6.4), 9.22 computer years on StarExec
  \item excludes result processors, StarExec overhead, glitches
  \end{itemize}
\end{frame}

@@

\begin{frame}{Division Winners}
  \pause
  \emph{Single Query}
  \begin{itemize}
  \item \emph{Bitwuzla}: {\small QF\_Bitvec, QF\_Equality+Bitvec}
  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith, Bitvec, Equality, Equality+LinearArith, Equality+MachineArith, Equality+NonLinearArith, FPArith, QF\_Equality, QF\_Equality+LinearArith, QF\_Equality+NonLinearArith, QF\_FPArith, QF\_LinearIntArith, QF\_LinearRealArith, QF\_NonLinearIntArith, QF\_NonLinearRealArith, QF\_Strings\end{minipage}
  \item \emph{iProver}: {\small Equality+NonLinearArith}
  \item \emph{SMTInterpol}: {\small QF\_Equality+LinearArith}
  \item \emph{UltimateEliminator+MathSAT}: {\small Equality+NonLinearArith}
  \item \emph{Vampire}: {\small Arith, Equality, Equality+NonLinearArith}
  \item \emph{Yices2}: {\tiny QF\_Bitvec, QF\_Equality, QF\_LinearIntArith, QF\_LinearRealArith, QF\_NonLinearIntArith}
  \end{itemize}

@@

\begin{frame}{Division Winners}
  \emph{Incremental}
  \begin{itemize}
  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith, Bitvec, Equality, Equality+LinearArith, Equality+NonLinearArith, FPArith, QF\_Equality, QF\_Equality+LinearArith, QF\_FPArith\end{minipage}
  \item \emph{OpenSMT}: {\small QF\_LinearRealArith}
  \item \emph{SMTInterpol}: {\small QF\_Equality+NonLinearArith,QF\_NonLinearIntArith}
  \item \emph{STP}: {\small QF\_Bitvec}
  \item \emph{Yices2}: {\small QF\_Equality+Bitvec,QF\_LinearIntArith}
  \end{itemize}
  \medskip

  \pause
  \emph{Model Validation (competitive only)}
  \begin{itemize}
  \item \emph{Bitwuzla}: {\small QF\_Bitvec}
  \item \emph{cvc5}: {\small QF\_LinearIntArith}
  \item \emph{Yices2}: {\small QF\_LinearRealArith}
  \end{itemize}
\end{frame}

>>>>

%%% Titel, Autor und Datum des Vortrags:
\title{SMT-COMP 2021\\
17th International Satisfiability Modulo Theory Competition}
\author{\emph{Haniel Barbosa} \and Jochen Hoenicke \and Fran\c{c}ois Bobot}
\date{Aug 11, 2022}

%% Institut
\institute{
  Universidade Federal de Minas Gerais, Brazil \and
  Albert-Ludwigs-Universit\"at Freiburg, Germany \and
  CEA List, France
}

@@

\newcommand\vitem{\vfill\item}

@@

  \begin{minipage}[b]{.6\textwidth}
    Annual competition for \emph{SMT solvers}\\
    on (a selection of) benchmarks from \emph{SMT-LIB}
  \end{minipage}%
  \begin{minipage}{.4\textwidth}
    \begin{block}{History}
      \begin{tabular}{rp{3cm}}
        \textbf{2005} & first competition \\
        \textbf{2013} & evaluation instead \\
        & of competition\\
        \textbf{2014} & since then hosted\\
        & by \emph{StarExec}
      \end{tabular}
    \end{block}
  \end{minipage}

  Goals:
  \begin{itemize}
  \item spur development of SMT solver implementations
  \item promote SMT solvers and their usage
  \item support the SMT-LIB project
    \begin{itemize}
    \item to promote and develop the SMT-LIB format
    \begin{itemize}
      \item model validation
      \item proof checking
    \end{itemize}
    \item to collect relevant benchmarks
    \end{itemize}
  \item engage and include new members
  \end{itemize}

@@

  \begin{columns}
    \begin{column}{0.4\textwidth}
      \begin{block}{Non-incremental}
        391\,363 instances {\small (+9680)}\\
        with 1 query each \\
        in 81 logics {\small (+2)}.
      \end{block}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{block}{Incremental}
        43\,285 instances {\small (+1)}\\
        with 33\,998\,935 queries {\small (+141)} \\
        in 39 logics.
      \end{block}
    \end{column}
    \begin{column}{0.08\textwidth}
    \end{column}
  \end{columns}
  \pause
    \begin{columns}
    \begin{column}{0.4\textwidth}
      \begin{block}{Selected Non-incremental}
        \only<2>{206\,932 instances}\only<3>{\textcolor{red}{206\,932}
          instances\\
          \textcolor{red}{We mistakenly ignored 9466 new benchmarks}
        }
      \end{block}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{block}{Selected Incremental}
        22\,300 instances
      \end{block}
    \end{column}
    \begin{column}{0.08\textwidth}
    \end{column}
  \end{columns}

@@

\begin{frame}[fragile]{SMT-COMP Tracks (experimental)}

  \emph{Model Validation}
  \begin{itemize}
    \item Division with quantifier-free floating-point logics
    \item Model validation with Dolmen (thanks to Gillaume Bury and Fran\c{c}ois
    Bobot)
  \end{itemize}
  \bigskip

  \emph{Cloud and Parallel Track} (sponsored by AWS, led by Mike Whalen)
  \begin{itemize}
  \item Solve a large problem over the cloud (or a big computer)
  \begin{itemize}
    \item 100 machines, 1600 cores, 6400 GB of memory (cloud)
    \item 64 cores, 256 GB of memory (parallel)
  \end{itemize}
  \item Solver answers sat/unsat/unknown
  \end{itemize}

  \pause\bigskip

  \emph{Proof Exhibition Track}
  \begin{itemize}
  \item Solver submitted together with a checker for unsatisfiability proofs
  \item No predefined format or checker
  \item No ranking
  \item Qualitative assessment
  \end{itemize}

\begin{frame}{Tracks, Solvers, Divisions, and Benchmarks}
  Teams: 21 (+3)
  \bigskip

  \begin{tabular}{c|r@{}l|r@{}l|c}
    Track & \multicolumn{2}{c|}{Solvers} & \multicolumn{2}{c|}{Divisions}  & Benchmarks \\
    \hline
    Single Query  &  22&(+3)  & 19&(+1)  & 93\,945 \\
    Incremental &  8&(+1)   & 17&(+2)  & 22\,300   \\
    Unsat Core  &  6&(-1)   & 18&(+1)  & 57\,245  \\
    Model Validation  &  8&(+1)    &  7& (+ 1 exp.)  & 32\,766  \\
    Proof Exhibition  &  &4    &  & 18 exp.  & 57\,245  \\
    \hline
    Parallel &   4&(+1)      &   &14 exp.  & 400 \\
    Cloud & 4&(-1)      &  &14 exp.  & 400 \\

  \end{tabular}
  \bigskip

  Number in parenthesis shows changes from 2021
\end{frame}

@@

  SMT-COMP 2022 participants rely on multiple reasoning frameworks:
  \begin{itemize}
  \item CDCL(T)
  \item mcSAT
  \item saturation
  \item automata
  \item finite domain
  \item CP
  \item local search
  \item besides wrappers extending the scope of existing solvers
  \end{itemize}

  \bigskip
  Six new solvers participated:
  \begin{itemize}
  \item NRA-LS   {\footnotesize (Liu et al.)}
  \item OSTRICH {\footnotesize (Chen et al.)}
  \item Yices-ismt {\footnotesize (Jia et al.)}
  \item Z3++ {\footnotesize (Cai et al.)}
  \item solsmt {\footnotesize (Reitwiessner and Soos)}
  \end{itemize}

@@

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-bitwuzla.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-colibri.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-cvc5.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-cvc5-cloud.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-nra-ls.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-opensmt.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-smtinterpol.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-solsmt.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-stp.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-verit.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-yices.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-yices-ismt.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-yices-qs.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-z3pp.pdf}}
\end{frame}
}

{
  \begin{frame}
    \frametitle{Other participants}
    \begin{itemize}
      \item Q3B
      \vitem SMT-RAT
      \vitem SMTS
      \vitem UltimateEliminatior+MathSAT
      \vitem Vampire
      \vitem Z3str4
    \end{itemize}
  \end{frame}
}

@@

  Submitted by organisers
  \begin{itemize}
  \item z3-4.8.17
  \item MathSAT 5.6.8
  \item Best solvers, per division, from previous years (23 Solvers)
  \end{itemize}
  \bigskip

  Submitted by participants
  \begin{itemize}
  \item Fixed solvers (OpenSMT, STP, Yices-ismt, Z3++,smtinterpol)
  \end{itemize}
\end{frame}

@@

\begin{frame}{Division Winners}
  \pause
  \emph{Single Query, sequential score}
  \begin{itemize}
  \item \emph{Bitwuzla}: {\small FPArith, QF\_Bitvec, QF\_Equality+Bitvec, QF\_FPArith}

  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith,
    Bitvec, Equality, Equality+LinearArith, Equality+MachineArith,
    Equality+NonLinearArith, QF\_Datatypes, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith, QF\_NonLinearRealArith, QF\_Strings\end{minipage}

  \item \emph{OpenSMT}: {\small QF\_LinearIntArith}

  \item \emph{SMTInterpol}: {\small QF\_Equality+LinearArith}

  \item \emph{Yices2}: {\small QF\_Equality, QF\_LinearRealArith}
  \end{itemize}

@@

\begin{frame}{Division Winners}
  \emph{Incremental}
  \begin{itemize}
\item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith,EqualityNonLinearArith,Equality
\item \emph{UltimateEliminator+MathSAT}: Equality+MachineArith
\item \emph{Bitwuzla}: FPArith, QF\_Bitvec, QF\_FPArith
\item \emph{Yices2}: QF\_Equality+Bitvec, QF\_Equality, QF\_LinearIntArith
\item \emph{SMTInterpol}: QF\_Equality+LinearArith, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith
\item \emph{OpenSMT}: QF\_LinearRealArith
  \end{itemize}
  \medskip

  \pause
  \emph{Model Validation (competitive only)}
  \begin{itemize}
\item \emph{Bitwuzla}: QF\_Bitvec, QF\_Equality+Bitvec,
\item \emph{smtinterpol}: QF\_Equality+LinearArith
\item \emph{Yices2}: QF\_Equality
\item \emph{Z3++}: QF\_LinearIntArith
\item \emph{OpenSMT}: QF\_LinearRealArith

\item experimental: QF\_FPArith : Bitwuzla, cvc5

  \end{itemize}
\end{frame}

\begin{frame}{Largest contribution}
  \begin{tabular}{r|c@{}lc@{}lc@{}l}
    &\textcolor{gold}{\textbf{1st Place}} &&
    \textcolor{silver}{\textbf{2nd Place}} &&
    \textcolor{bronze}{\textbf{3rd Place}}\\
    \hline
    \emph{Single Query}\\
    seq & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
    par & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
    sat & cvc5&{\tiny(Eq+LA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
    unsat & cvc5&{\tiny(Eq+MA)} & Z3++&{\tiny(QF\_NonLIA)} & OSTRICH&{\tiny(QF\_Strings)}\\
    24 &  Vampire&{\tiny(Eq+NA)} & Vampire&{\tiny(Equality)} & Yices2&{\tiny(QF\_LinIA)}\\[3pt]
    \pause
    \emph{Incremental}\\
    par & cvc5&{\tiny(Eq+NA)} &Yices2&{\tiny(QF\_Eq+LA)}
    &SMTInterpol&{\tiny(QF\_Eq+NA)}\\[3pt]
    \pause

    \emph{Unsat Core}\\
    seq & cvc5&{\tiny(Eq+LA)} &
    Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\

    par &  cvc5&{\tiny(Eq+NA)}&
    Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\
\\[3pt]
    \pause
    \emph{Model Validation}\\
    seq &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
        & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
    par &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
        & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
  \end{tabular}
\end{frame}
